\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, we solve \eqref{KineticProx} by recursively updating the probability-weighted scattered point clouds $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\tilde{\bm{x}}_{k}^{i}:=\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N, \quad k\in\mathbb{N}.$$
Thus, $\tilde{\varrho}_{k}^{i}$ is the joint PDF value obtained from \eqref{KineticProx} at $\bm{x}_{k}^{i}$, the $i$th state sample at the $k$th time step. The schematic of the algorithm is shown in Fig. \ref{fig:BlockDiagm}.

>>>>

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, we solve \eqref{KineticProx} by recursively updating the probability-weighted scattered point clouds $\{\tilde{\bm{x}}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\tilde{\bm{x}}_{k}^{i}:=\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N, \quad k\in\mathbb{N}.$$
Thus, $\tilde{\varrho}_{k}^{i}$ is the joint PDF value obtained from \eqref{KineticProx} at $\tilde{\bm{x}}_{k}^{i}$, the $i$th state sample at the $k$th time step. The schematic of the algorithm is shown in Fig. \ref{fig:BlockDiagm}.
